``Colloidal rain'' as a novel route to crystallization via viscoelastic phase separation

### 2015-10-05 science/crystal_gel_letter2.tex
Fixed the equation for the radius of gyration.

As described above and also in Methods, salt injection initiates liquid-gas phase separation of the colloidal suspension. 
All samples share the same early stages of spinodal decomposition. 
Due to strong dynamical asymmetry between colloids and the solvent \cite{tanaka1999colloid}, the colloidal particles start aggregating, 
eventually forming a percolating network. Thus, a dense network (liquid) coexists with freely diffusing monomers (gas). 
The topology of the network is similar to all our samples at the initial stages.
This is shown for example in Fig.~\ref{fig:phase_separation}B, where we plot the radius of gyration of colloidal clusters ($R_g$)
as a function of the cluster size ($s$) at the percolation point. Two particles belong to the same cluster if their distance is
within the first peak of the radial distribution function. All samples show the same scaling law, which is compatible with
the random gelation universality class exponent ($D=2.53$) as shown by the dashed line in Fig.~\ref{fig:phase_separation}B.

>>>>

As described above and also in Methods, salt injection initiates liquid-gas phase separation of the colloidal suspension. 
All samples share the same early stages of spinodal decomposition. 
Due to strong dynamical asymmetry between colloids and the solvent \cite{tanaka1999colloid}, the colloidal particles start aggregating, 
eventually forming a percolating network. Thus, a dense network (liquid) coexists with freely diffusing monomers (gas). 
The topology of the network is similar to all our samples at the initial stages.
This is shown for example in Fig.~\ref{fig:phase_separation}B, where we plot the radius of gyration of colloidal clusters ($R_g$)
as a function of the cluster size ($s$) at the percolation point. Two particles belong to the same cluster if their distance is
within the first peak of the radial distribution function. All samples show the same scaling law, $R^2_{\rm g}\sim s^{2/D}$, which is compatible with
the random gelation universality class exponent ($D=2.53$) as shown by the dashed line in Fig.~\ref{fig:phase_separation}B.
